\chapter{Conclusion}



	From the beginning of this project, the intent has been to understand how plausible it would be to determine if there are predictable market forces acting within a given industry. The continued recurrence of the same highly connected companies implies the market forces that govern these few companies in turn govern their respective industries. Through the PCA reduction of several variables the graphs constructed have given great insight into how these forces can sway even the largest companies over the years. From the housing market affecting the hardware industry, to near identical movements within the oil industry and to delayed tough near mirroring moves in the automotive industry.\\
\newline

	These various phenomena within each graph can all be attributed to a major event affect each company. From an acquisition that went well or poorly to an unexpected and expensive recall each change in trajectory has a tangible meaning. These finding give credit to the next phase of this research.\\
\newline

	The next goal for this research into industry force is to move from a descriptive model to a predictive one.  The scope of the study will eventually be expanded to include more companies to build a predictive model. Ideally the model, given a change in trajectory, will be able to predict what the next points in the graph will be. With enough predictions of companies in a given industry it may be possible to determine in what direction an industry and its respective companies will be moving.\\
\newline

